Draft

### 2016-11-08 Draft/sections/misc-math.tex
Minor updates to physicist-taper.sty. Adding some pitfalls to math in Draft.

>>>>

\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}

    The $k$-th component $\psi_k$ of the transpose of $(A\phi)^i = A^i_k
    \phi^k$ is still $A^i_k \phi^k$, although we have to be careful about
    the position of the index.

    \subsubsection{Transpose}
    \label{sec:Transpose}

    In matrix theory, if we ahave the following structure:
    $$\braket{x,y} := x y$$
    here $x,y$ are regarded as two column vectors in vector space $V$.
    Then the transpose of a linear transformation $A:V\to V$ is defined
    as
    \begin{defi}[Transpose]
    \nomenclature{Transpose}{\nomrefpage.}
        $\tensor[^t]{A}{}:V^* \to V^*$ is such that:
        \begin{equation}
            \braket{x,Ay} = \braket{\tensor[^t]{A}{}x,y}
        \end{equation}
        for any $x,y\in V$.
    \end{defi}

    In my notation, it maps $x^n\to A^m_n x^m$, or $x_n\to A^m_n x_m$.
    (My notation is non-standard, but I think it expresses the idea).
